---
title: "day 9 comp"
author: "Kiran Favre"
date: "2022-08-18"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)

```

## Google workshop

Practice:

Example 1) with data sets a and b. Each contain the same attributes
(columns). Identify which records (rows of data) in data table a are not
contained in data table b.

```{r}
a <- data.frame(month = c("October", "November", "December", "January", "February"), season = c("Fall", "Fall", "Winter", "Winter", "Winter"), daylight_savings = c("yes", "partly", "no", "no", "no"))

b <- data.frame(month = c("October", "December", "February"), season = c("Fall", "Winter", "Winter"), daylight_savings = c("yes", "no", "no"))

a_not_b <- anti_join(x = a, y = b, by = "month") #anti_join returns all rows from x without a match in y
```

Example 2) Modify the following code such that it sorts any blue animals
from the animals vector into the blue_animals vector.

```{r}
##~~~~~~~~~~~~~~~~~~~~~~~~~~~
##  ~ vector of animals  ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~
animals <- c("blue tang", "red panda", "Blue jay",
             "green sea turtle", "blue morpho butterfly", 
             "Blue iguana", "Red squirrel")
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##  ~ initialize empty vector to store blue-colored animals  ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
blue_animals <- c()
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##  ~ sort blue animals into their own list  ----
##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
for (i in 1:length(animals)){
  current_animal <- animals[i]
  if(isTRUE(str_detect(current_animal, fixed("blue", ignore_case = TRUE)))){  
    message("The '", current_animal, "' is a blue animal")
    blue_animals <- append(blue_animals, current_animal)
  }
}
#taking a look at 1st animal name, if blue is in first item, print this message, and store in blue animals vector
# Problem: cases-- we need to be able to ignore the case because some are upper case
  # can also use "(?i)blue" in the str_detect fxn
# Problem: the values being saved to blue_animals is only saving the last value
  # soln: use append
```

Example 3: Modify code to recreate given plot

```{r}

ggplot(data = na.omit(penguins), aes(x = species, y = body_mass_g, shape = sex, fill = species)) +
  geom_point(alpha = 0.5, position = position_jitterdodge(dodge.width = 0.5)) + 
  # means & standard devs
  stat_summary(mapping = aes(color = species), 
               position = position_dodge(width = 0.5),
               fun = "mean", 
               geom = "point", size = 4) +
  stat_summary(mapping = aes(color = species),
               position = position_dodge(width = 0.5),
               fun = "mean", geom = "errorbar", size = 1, width = 0.2,
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) +
  # change colors/shapes
  scale_color_manual(values = c("orange", "purple", "cyan4")) + 
  scale_shape_manual(values = c(15, 16), name = "Sex") + 
  # add nicer axis labels + title + caption
  labs(x = "Penguin Species", 
       y = "Body Mass (g)",
       title = "Body mass of female vs. male adelie, chinstrap, and gentoo penguins",
       subtitle = "Colored points represent mean body mass (± SD)",
       caption = "Data Source: Dr. Kristen Gorman, LTER Palmer Station") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0, size = 14),
        axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(color = "black", size = 14),
        plot.caption = element_text(size = 7, hjust = 1, color = "gray", face = 
                                      "italic"),
        panel.border = element_rect(color = "black", size = 0.7, fill = NA))
```

-   dodge vs jitter_dodge: jitter put some space between points, but
    dodge spaces out errything
